### 2021-12-06 documents/sections/verbs.tex
rewriting section 4

>>>>

\subsection{Summary}
\label{sec:verbsummary}
In \cref{sec:verbs}, the verbs which were unaffected by the extensions in \cref{sec:extensions} were reconstructed, and affected reflexes in the languages under discussion were identified, where possible.
\cref{tab:overview} gives an overview of what verbs were affected by which extensions, except for \obj{e}-initial \akuriyo verbs unaffected by the extension of \obj{k-}, as they are a large and predictable group.
In some cases, the verb does not occur at all or just not in first person forms (–), in others the first person form is unknown (?), and in the case of \qu{to go down} the question of affectedness is not meaningfully answerable (\textsc{n/a}), for any of the reasons discussed in \cref{sec:godown}.
Every \checkmark stands for a verb affected by an extension, while × represents conservatively inflected verbs.
This overview makes clear just how pervasive the tendency for these verbs to resist innovative markers is, as they do so in different languages.

\input{floats/overview.tex}

It is astonishing that the same 1-7 verbs retain their old first person marker in 6 distinct developments, while a plethora of regular \gl{s}\textsubscript{(\gl{a})} verbs take on innovative markers.
This suggest that there is some strong motivation for these verbs to not be affected by innovative markers.
The question arises what properties unite these verbs and make them so conservative across different Cariban languages.
Possible answers to this question will be discussed in \cref{sec:motivations}, using \posscite{bybee1985morphology} network model of morphology.
